Critical Temperature of YBCO and BSCCO Superconductors

### 2014-12-12 Draft.tex
edit methods

\section{Procedure}
The YBCO and BSCCO superconductors were obtained from Colorado Superconductor Inc. Each superconductor  is contained in a brass casing with three pairs of leads. 
One pair was for attaching to the current source, another pair was used to measure voltage across the superconductor, and the last pair that of the thermocouple inside the casing. 
The thermocouple produces a voltage when one part of the circuit has a temperature different from a reference point.
We used different methods to measure the critical temperature of the two superconductors.
For the YBCO, we connected it to a source with an alternating current of $\pm$1 mA. 
The voltage across the YBCO sample, $V_{\textrm{YBCO}}$, and the voltage across the thermocouple \textcolor{magenta}{junction}, $V_{T}$ were measured with two nanovoltmeters. \textcolor{blue}{you should explain the point of reversing the current and how this helps more accurately determine the true }$\Delta V$
The voltage across the YBCO sample was converted into a resistance reading by the nanovoltmeter.
 \textcolor{blue}{Include circuit diagrams.}

@@

We used a two-phase lock-in amplifier for the BSCCO experiment. An AC circuit \textcolor{magenta}{set up for the} measurement of resistance \textcolor{magenta}{is also susceptible to (or includes) } contributions from \textcolor{magenta}{parasitic capacitances and inductances between wires and to ground (or capacitors and inductors)}. 
Although there are no explicit capacitors or inductors in our circuit, they are effectively present due to the electrical cables used \textcolor{magenta}{and construction of the circuit}. 
The lock-in amplifier allows us to extract the resistance of superconductor from the other contributions because the resistance will be in phase with the \textcolor{red}{signal}, while the contributions of capacitors and inductors will be out of phase. \textcolor{blue}{the in phase component IS your signal. I think you mean that the voltage drop across the sample due to its resistance will be in phase with the applied ac voltage from the oscillator, but of course you can say this more succinctly}. 
Since the resistance of the BSCCO at room temperature is on the order of m$\Omega$s, we can generate an AC current with an RMS amplitude of approximately $\pm$1 mA in the circuit by connecting the BSCCO in series with a 1 k$\Omega$ resistor, and with a AC voltage source with an RMS amplitude of 1 V.

>>>>

\section{Procedure}
The YBCO and BSCCO superconductors were obtained from Colorado Superconductor Inc. Each superconductor  is contained in a brass casing with three pairs of leads. 
One pair was for attaching to the current source, another pair was used to measure voltage across the superconductor, and the last pair that of the thermocouple inside the casing. 
The thermocouple produces a voltage when one part of the circuit has a temperature different from a reference point.
We used different methods to measure the critical temperature of the two superconductors.
For the YBCO, we connected it to a source with an alternating current of $\pm$1 mA. The alternating current  
The voltage across the YBCO sample, $V_{\textrm{YBCO}}$, and the voltage across the thermocouple junction, $V_{T}$ were measured with two nanovoltmeters. \textcolor{blue}{you should explain the point of reversing the current and how this helps more accurately determine the true }$\Delta V$
The voltage across the YBCO sample was converted into a resistance reading by the nanovoltmeter.
 \textcolor{blue}{Include circuit diagrams.}

@@

We used a two-phase lock-in amplifier for the BSCCO experiment. An AC circuit set up for the measurement of resistance is susceptible to contributions from capacitors and inductors. 
Although there are no explicit capacitors or inductors in our circuit, they are effectively present due to the electrical cables used and construction of the circuit. 
The lock-in amplifier allows us to extract the resistance of superconductor from the other contributions. Since changes in $V_{BSCCO}$ due to resistance are in phase with applied voltage and the contributions of capacitors and inductors are out of phase, our signal is just the in phase component.  
Since the resistance of the BSCCO at room temperature is on the order of m$\Omega$s, we can generate an AC current with an RMS amplitude of approximately $\pm$1 mA in the circuit by connecting the BSCCO in series with a 1 k$\Omega$ resistor, and with a AC voltage source with an RMS amplitude of 1 V.
